The Globular Cluster System of the Auriga Simulations

### 2018-12-29 Partial/FeH_logM.tex
Mass-weighted FeH binning v1.0 done

        1      & 3      & -1.5   & -1.0   & 12     & 1.9e+06 & 6.27       \\
        1      & 3      & -1.0   & -0.5   & 9      & 7.7e+05 & 5.89       \\

@@

        3      & 8      & -1.5   & -1.0   & 12     & 2.4e+06 & 6.37       \\
        3      & 8      & -1.0   & -0.5   & 10     & 2.5e+06 & 6.39       \\
        3      & 8      & -0.5   & -0.3   & 6      & 1.9e+06 & 6.29       \\

@@

        8      & 15     & -1.5   & -1.0   & 6      & 1.9e+06 & 6.27       \\

@@

        3      & 8      & -1.5   & -1.0   & 5      & 9.1e+05 & 5.96       \\

@@

        8      & 15     & -1.5   & -1.0   & 4      & 1.3e+06 & 6.13       \\

@@

\section{Distribution of metallicity [Fe/H]}
\label{sec:FeH}

@@

\newpage
\bibliographystyle{../mnras}
\bibliography{../AurigaGCS}

>>>>

        1      & 3      & -1.5   & -1.0   & 15     & 1.9e+06 & 6.28       \\
        1      & 3      & -1.0   & -0.5   & 10     & 8.2e+05 & 5.91       \\

@@

        3      & 8      & -1.5   & -1.0   & 15     & 2.8e+06 & 6.44       \\
        3      & 8      & -1.0   & -0.5   & 11     & 2.8e+06 & 6.44       \\
        3      & 8      & -0.5   & -0.3   & 7      & 1.9e+06 & 6.29       \\

@@

        8      & 15     & -1.5   & -1.0   & 7      & 2.4e+06 & 6.38       \\

@@

        3      & 8      & -1.5   & -1.0   & 6      & 1.1e+06 & 6.03       \\

@@

        8      & 15     & -1.5   & -1.0   & 5      & 1.9e+06 & 6.27       \\

@@

\afterpage{%
\section{Distribution of metallicity [Fe/H]}
\label{sec:FeH}
\thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-all}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit0}.png}
    \caption{
        \scriptsize \emph{Left:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} There seems to be a trent of constant mass increase with
        increasing metallicity in the range -3 to -1, and roughly 1 order of 
        magnitude scatter in mass normalization. We use linear regression to 
        obtain log$_{10}$(mass normalization) (i.e. we fit $a\cdot(x+3) + b$)
        \label{fig:todo1}
    }

    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit1}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
    \caption{
        \scriptsize \emph{Left:} Scatter plot of log$_{10}$(mass normalization)
        [i.e. $b$ obtained above] against the virial mass M$_{200,c}$ of the 
        Auriga haloes. We use linear regression to see whether there is a 
        correlation, and find $a_2 = 0.00388$, $b_2 = 6.597$. Colours indicate 
        resolution: L3 red, L4 green, and L5 blue.
        \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
        `central' x value; yellow region 1$\sigma$ interval; blue dashed lines 
        intrinsic scatter. Fake Error bars (1\% of the obtained values).
        \label{fig:todo2}
    }

    { \centering
    \includegraphics[width=0.4\textwidth]{{logMFeH_OldStars_normalization_fit2}.png}
    \caption{
        \scriptsize TODO: corner plot of the MCMC. Conclusion: there is a positive 
        correlation of the normalization of old stellar mass with the virial
        mass $M_{200,c}.$
        \label{fig:todo3}
    }
    }
\end{figure*}
\clearpage
}
\clearpage

\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-errorbar}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-hist2d}.png}
    \caption{
        % Au3-6, 16, 21, 23, 24, 27; Au4-1-30; Au5-6, 9 16 24
        \emph{Left:} Mean value of all 40 simulations in orange.
        \emph{Right:} Colorbar shows the number of simulations that fall in
        (arbitrary) bins in y-direction.
        \label{fig:todo4}
    }

    \includegraphics[width=0.49\textwidth]
        {{logMFeH_OldAccreted_plot-hist2d-with-mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{logMFeH_OldInsitu_plot-hist2d-with-mean}.png}
    \caption{
        \emph{Left:} Mass-weighted [Fe/H] distribution of 
        \textbf{Old accreted} (age $>$~10~Gyr) star particles.
        Solid orange line shows the mean of all old star particles in all Auriga
        simulation. The dotted orange line shows the mean of all star particles
        in all Auriga simulations (i.e. not enforcing an age cut).
        \emph{Right:} Mass-weighted [Fe/H] distribution of \textbf{Old insitu} 
        (age $>$~10~Gyr) star particles. 
        \emph{Both / Conclusion:} The metallicity range $-3 <$ [Fe/H] $< -1$ is
        only populated star particles older than ten Gyr; [Fe/H] $> -1$ is dominated
        by star particles younger than 10~Gyr (two orders of magnitude difference). 
        Furthermore, the old accreted star particles contribute most significantly 
        to the range $-3 <$ [Fe/H] $< -1$, and the contribution of the old insitu
        star particles at these metallicities declines steeper with declining
        metallicity than the old accreted population. The old insitu population
        provides the dominant contribution of the old population for 
        [Fe/H] $> -1$.
        \label{fig:todo5}
    }
\end{figure*}
\clearpage

\begin{figure*}[h!]
    \includegraphics[width=\textwidth]{{logMFeH}.png}
    \caption{
        This figure summarises above findings. TODO: write caption for 
        paper.
        \label{fig:todo6}
    }
\end{figure*}

@@

\bibliographystyle{../mnras}
\bibliography{../AurigaGCS}
